Pool Model

### 2023-12-20 pool_model.tex
slightly correct description

        Specifying all parameters here would requrie a much larger table.
        For the full information, we refer to the supplementary material~\ref{sec:supplement-full-parameters}.

>>>>

        To view, how these parameters are stored inside a cell-agent, we refer to the supplementary material~\ref{sec:supplement-full-parameters}.
